---
title: "Use Case: Analyzing Synthetic Sales Data with tstodfpkg"
author: "Abiyu Giday"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use Case: Analyzing Synthetic Sales Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
library(tstodfpkg)
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```
<style>
:not(pre) > code {
  color: #a11f0c !important;
  font-weight: bold;
  font-size: 1.2em;
  }
  h1 {
  color: #556dac;
  font-size: 2em;
  font-weight: bold;
}
h2 {
  color: #68829e;
  font-size: 1.6em;
  font-weight: bold;
}
h3 {
  color: #7f8c8d;
  font-size: 1.2em;
  font-weight: bold;
}
h4 {
  color: #7f8c8d;
  font-size: 1em;
  font-weight: bold;
}
</style>

# Analyzing Time Series Sales Data

This vignette demonstrates how to use `tstodfpkg` to analyze the `synth_gap` dataset, a synthetic quarterly sales time series. We will show `ts_to_df` working with both the original `ts` structure and the converted `data.frame`, comparing the results to highlight its versatility.

## Visualizing Trends with Time Series

Load the dataset and plot the time series to identify trends:
```{r, fig.width = 7, fig.height = 5}
data(synth_gap)
plot(synth_gap, main = "Synthetic Sales Trend", xlab = "Time", ylab = "Sales", type = "l")
```

## Analyzing with Data Frame Using dplyr and ggplot2

Convert the time series to a data frame and use `dplyr` for aggregation:
```{r}
df <- ts_to_df(synth_gap, name = "Sales")
library(dplyr)
sales_summary <- df %>% group_by(Period) %>% summarise(Avg_Sales = mean(Sales))
print(sales_summary)
```

Visualize the quarterly sales with `ggplot2`:
```{r, fig.width = 7, fig.height = 5}
library(ggplot2)

ggplot(df, aes(x = Year, y = Sales, color = Period)) + 
  geom_line() + 
  #facet_wrap(~ Year, ncol = 4) + 
  theme_minimal() + 
  theme(legend.position = "top") + 
  labs(title = "Quarterly Sales Over time")
```

This approach leverages the `data.frame` structure for flexible manipulation and enhanced visualization, making it ideal for detailed sales pattern analysis.
